Synthesizing Quotient Lenses

### 2018-03-13 papers/QuotientLenses/main.tex
minor textual changes:

%\newcommand{\QOpt}{Optician_Q}
\newcommand{\QOpt}{QRE-enhanced Optician}
\newcommand{\OpticianRuntime}{\textbf{OO}}
\newcommand{\QREOptician}{\textbf{OQ}}
\newcommand{\SystemOnOptician}{\textbf{QO}}
\newcommand{\SystemOnBenchmarks}{\textbf{QQ}}
\newcommand{\cd}[1]{\lstinline[backgroundcolor=\color{white}]$#1$}

@@

\begin{figure}[t]
\includegraphics{generated-graphs/asts.eps}
\caption{AST node measurements for each of the three approaches
on each of the 10 non-bijective benchmark problems.
QRE Synthesis requires far fewer AST nodes than the other
two approaches. \ksf{Anders, is there an order to the benchmarks in
this list?  It might be useful to list them in order of increasing
complexity of the format, perhaps measured by the sum of the number of
AST nodes in the source and target format descriptions.  It seems
better to have some order than just listing them randomly, even if it
doesn't show much interesting.}}
%%\caption{Count of benchmark programs definable using a given AST count. We find
%%that it takes far fewer AST nodes to define benchmark lenses using QRE
%%synthesis than with Optician without QRE synthesis or without synthesis.}
\label{fig:asts}
\end{figure}

@@

\ksf{Anders: are these figures up to date?}
Figure~\ref{fig:asts} shows each of these measures for the 10
non-bijective problems in the benchmark suite.  On
average, \canonizeAndSpecSize{} used~44\% more AST nodes
than \QRESize{}, requiring an average of~237 more AST nodes. On 
average, \LensAndSpecSize{} used~193\% more AST nodes than \QRESize{}, requiring an
average of~1267 more AST nodes. These figures suggest that introducing QREs saves
programmers significant effort compared to both pre-QRE Optician and basic
Boomerang.

@@

\begin{figure}[t]
\centering
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{generated-graphs/times_opt}
\caption{}
\label{subfig:lenssize}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}
\includegraphics{generated-graphs/times_new.eps}
\caption{}
\label{subfig:examplesused}
\end{subfigure}
\caption{Runtimes measurements. In (a), we run the
  original version of Optician (\OpticianRuntime{}) and \QOpt{}
  (\QREOptician{}) on the Optician benchmarks.  We find that there is only a negligible
  performance overhead incurred by using QREs. 
  In (b), we run \QOpt{} on the 10 Optician benchmarks
  previously edited to make them bijective, after removing those edits
  (In other words, we restored them to their original state and then
  ran \QOpt{}). 
  We find that \QOpt{} is able to
  synthesize all quotient lenses in under 20 seconds, and typically finishes in
  under 5 seconds.}
\label{fig:times}
\end{figure}

@@

Second, how much time does it take for \QOpt{} to synthesize a QRE
lens when running on a non-bijective benchmark problem?  
Figure~\ref{fig:times}(b) shows the amount of time required to infer a
lens for each of the 10 benchmark programs.  
We find that \QOpt{} is able to synthesize all quotient lenses in
under 20~seconds, and typically finishes in under 5~seconds.

>>>>

%\newcommand{\QOpt}{Optician_Q}
\newcommand{\QOpt}{QRE-enhanced Optician}
\newcommand{\OpticianRuntime}{\textbf{Optician}}
\newcommand{\QREOptician}{\textbf{Optician\textsubscript{Q}}}
\newcommand{\SystemOnOptician}{\textbf{QO}}
\newcommand{\SystemOnBenchmarks}{\textbf{QQ}}
\newcommand{\cd}[1]{\lstinline[backgroundcolor=\color{white}]$#1$}

@@

\begin{figure}[t]
\includegraphics{generated-graphs/asts.eps}
\caption{AST node measurements for each of the three approaches
on each of the 10 non-bijective benchmark problems.
QRE Synthesis requires far fewer AST nodes than the other
two approaches.}
%%\caption{Count of benchmark programs definable using a given AST count. We find
%%that it takes far fewer AST nodes to define benchmark lenses using QRE
%%synthesis than with Optician without QRE synthesis or without synthesis.}
\label{fig:asts}
\end{figure}

@@

Figure~\ref{fig:asts} shows each of these measures for the 10
non-bijective problems in the benchmark suite.  On
average, \canonizeAndSpecSize{} used~44\% more AST nodes
than \QRESize{}, requiring an average of~237 more AST nodes. On 
average, \LensAndSpecSize{} used~193\% more AST nodes than \QRESize{}, requiring an
average of~1267 more AST nodes. These figures suggest that introducing QREs saves
programmers significant effort compared to both pre-QRE Optician and basic
Boomerang.

@@

\begin{figure}[t]
\centering
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{generated-graphs/times_opt}
\caption{}
\label{subfig:lenssize}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}
\includegraphics{generated-graphs/times_new.eps}
\caption{}
\label{subfig:examplesused}
\end{subfigure}
\caption{Runtimes measurements. In (a), we run the
  original version of Optician (\OpticianRuntime{}) and \QOpt{}
  (\QREOptician{}) on the Optician benchmarks.  We find that there is only a negligible
  performance overhead incurred by using QREs. 
  In (b), we run \QOpt{} on the 10 Optician benchmarks
  previously edited to make them bijective, after removing those edits
  (In other words, we restored them to their original state with QREs
  and then ran \QOpt{}). 
  We find that \QOpt{} is able to
  synthesize all quotient lenses in under 10 seconds, and typically finishes in
  under 5 seconds.}
\label{fig:times}
\end{figure}

@@

Second, how much time does it take for \QOpt{} to synthesize a QRE
lens when running on a non-bijective benchmark problem?  
Figure~\ref{fig:times}(b) shows the amount of time required to infer a
lens for each of the 10 benchmark programs with nontrivial quotients.  
We find that \QOpt{} is able to synthesize all quotient lenses in
under 10~seconds, and typically finishes in under 5~seconds.
